\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
add comment on pre populated relations

@@

\section*{Future Work and Conclusion}
In this paper, we have introduced \textit{Red Oak}, a SDN library for proactively generating a dynamic controller from an arbitrary programmer-defined policy in a general purpose programming language.
\textit{Red Oak} provides programmers the abstraction that their centralized policy will run on each 
new packet entering the network, while alleviating for the programmer need to consider
how to split the decision logic between to switches and the controller.

>>>>

While we currently start the simulation with empty relation, \lstinline|run| could easily be extended to initialize the controller with pre-populated relations.

@@

\section*{Conclusion}
In this paper, we have introduced \textit{Red Oak}, a SDN library for proactively generating a dynamic controller from an arbitrary programmer-defined policy in a general purpose programming language.
\textit{Red Oak} provides programmers the abstraction that their centralized policy will run on each 
new packet entering the network, while alleviating for the programmer need to consider
how to split the decision logic between to switches and the controller.
